Data Exploration: IUCN and AquaMaps

### 2015-12-21 data_explore/data_explore.Rmd
rescaled graphs and graph titles

ggsave(file.path(dir_fig, 'AreaRatiovsPercOverlap.png'), width = 6, height = 4)

@@

print(barchart_spp_gp_quads)
ggsave(plot = barchart_spp_gp_quads,
       filename = file.path(dir_fig, 'barchart_spp_gp_quads.png'),
       width = 6, height = 4)

@@

print(barchart_spp_risk_quads)
ggsave(plot = barchart_spp_risk_quads,
       filename = file.path(dir_fig, 'barchart_spp_risk_quads.png'),
       width = 6, height = 1.5)

@@

taxa_df_long2 <- taxa_df %>%
  dplyr::select(class, AquaMaps = n_am_class_solo, IUCN = n_iucn_class_solo, Both = n_class_both) %>%
  gather(dataset, n_spp, AquaMaps:Both) %>%
  group_by(class) %>%
  mutate(n_total = sum(n_spp, na.rm = TRUE),
         percent = n_spp/n_total * 100)
bar_taxa2 <- ggplot(taxa_df_long2, aes(x = class, y = percent, fill = dataset)) +
  ggtheme_plot + 
  geom_bar(stat = 'identity', alpha = .5) +
  scale_fill_manual(values = c('AquaMaps' = 'red', 'Both' = 'mediumorchid', 'IUCN' = 'blue')) +
  geom_text(aes(label = sprintf('n = %s', n_total), y = 3), 
            size = 3, angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) + 
  labs(x = 'Class', y = 'Percent of mapped species',
       title = 'Distribution of species maps by taxonomic group (class)')
print(bar_taxa2)
ggsave(filename = file.path(dir_fig, 'bar_by_taxa_all.png'), height = 4, width = 8)

taxa_df_long3 <- taxa_df %>%
  dplyr::select(class, AquaMaps = n_am_class_solo_ass, IUCN = n_iucn_class_solo, Both = n_class_both) %>%
  gather(dataset, n_spp, AquaMaps:Both) %>%
  group_by(class) %>%
  mutate(n_total = sum(n_spp, na.rm = TRUE),
         percent = n_spp/n_total * 100)
bar_taxa3 <- ggplot(taxa_df_long3, aes(x = class, y = percent, fill = dataset)) +
  ggtheme_plot + 
  geom_bar(stat = 'identity', alpha = .5) +
  scale_fill_manual(values = c('AquaMaps' = 'red', 'Both' = 'mediumorchid', 'IUCN' = 'blue')) +
  geom_text(aes(label = sprintf('n = %s', n_total), y = 3), 
            size = 3, angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) +
  labs(x = 'Class', y = 'Percent of mapped and assessed species',
       title = 'Distribution of species maps by taxonomic group (class)')
print(bar_taxa3)
ggsave(filename = file.path(dir_fig, 'bar_by_taxa_assessed.png'), height = 4, width = 8)

>>>>

ggsave(file.path(dir_fig, 'AreaRatiovsPercOverlap.png'), width = 6, height = 3.5)

@@

print(barchart_spp_gp_quads)
ggsave(plot = barchart_spp_gp_quads,
       filename = file.path(dir_fig, 'barchart_spp_gp_quads.png'),
       width = 6, height = 3.5)

@@

print(barchart_spp_risk_quads)
ggsave(plot = barchart_spp_risk_quads,
       filename = file.path(dir_fig, 'barchart_spp_risk_quads.png'),
       width = 6, height = 1.75)

@@

taxa_df_long2 <- taxa_df %>%
  dplyr::select(class, AquaMaps = n_am_class_solo, IUCN = n_iucn_class_solo, Both = n_class_both) %>%
  gather(dataset, n_spp, AquaMaps:Both) %>%
  group_by(class) %>%
  mutate(n_total = sum(n_spp, na.rm = TRUE),
         percent = n_spp/n_total * 100)
bar_taxa2 <- ggplot(taxa_df_long2, aes(x = class, y = percent, fill = dataset)) +
  ggtheme_plot + 
  geom_bar(stat = 'identity', alpha = .5) +
  scale_fill_manual(values = c('AquaMaps' = 'red', 'Both' = 'mediumorchid', 'IUCN' = 'blue')) +
  geom_text(aes(label = sprintf('n = %s', n_total), y = 3), 
            size = 3, angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) + 
  labs(x = 'Class', y = 'Percent of mapped species',
       title = 'Species maps by taxonomic class')
print(bar_taxa2)
ggsave(filename = file.path(dir_fig, 'bar_by_taxa_all.png'), height = 3, width = 6)

taxa_df_long3 <- taxa_df %>%
  dplyr::select(class, AquaMaps = n_am_class_solo_ass, IUCN = n_iucn_class_solo, Both = n_class_both) %>%
  gather(dataset, n_spp, AquaMaps:Both) %>%
  group_by(class) %>%
  mutate(n_total = sum(n_spp, na.rm = TRUE),
         percent = n_spp/n_total * 100)
bar_taxa3 <- ggplot(taxa_df_long3, aes(x = class, y = percent, fill = dataset)) +
  ggtheme_plot + 
  geom_bar(stat = 'identity', alpha = .5) +
  scale_fill_manual(values = c('AquaMaps' = 'red', 'Both' = 'mediumorchid', 'IUCN' = 'blue')) +
  geom_text(aes(label = sprintf('n = %s', n_total), y = 3), 
            size = 3, angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) +
  labs(x = 'Class', y = 'Percent of assessed mapped species',
       title = 'Species maps by taxonomic class, Red List-assessed only')
print(bar_taxa3)
ggsave(filename = file.path(dir_fig, 'bar_by_taxa_assessed.png'), height = 3, width = 6)

### 2015-12-21 data_explore/data_explore_am_thresh.Rmd
rescaled graphs and graph titles

ggsave(file.path(dir_fig, 'AMThreshold.png'), width = 6, height = 4)
```

@@

ggsave(file.path(dir_fig, 'AMThreshold2.png'), width = 6, height = 4)

@@

ggsave(file.path(dir_fig, 'scatter_AMThreshold.png'), width = 6, height = 4)

@@

ggsave(file.path(dir_fig, 'ribbon_AMThreshold.png'), width = 6, height = 4)

>>>>

ggsave(file.path(dir_fig, 'AMThreshold.png'), width = 6, height = 3.5)
```

@@

ggsave(file.path(dir_fig, 'AMThreshold2.png'), width = 6, height = 3.5)

@@

ggsave(file.path(dir_fig, 'scatter_AMThreshold.png'), width = 6, height = 3.5)

@@

ggsave(file.path(dir_fig, 'ribbon_AMThreshold.png'), width = 6, height = 3.5)
